Stage-Splitting a Modal Language

### 2014-06-19 paper/paper.tex
fixed the build and made figures files
added new code examples for future explanatory use
Reworked file structure a little.
move figures to a subdirectory
splitting up figures into separate files
miscellaneous cleanup
major reorganizing/rewriting of section 3.
adding some code formatting
adding hats

\documentclass{sigplanconf}

@@

\usepackage{amsmath}
%\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{mathpartir}
\usepackage{mathabx}
\usepackage{listings}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}

@@

\input {macros}
\input {grammars}
\input {abstract}
\input {intro}
\input {relatedwork}
\input {semantics}
\input {splitting}

@@

\titlebanner{banner above paper title}        % These are ignored unless
\preprintfooter{short description of paper}   % 'preprint' option specified.

@@

\input{intro}
\input{relatedwork}
\input{semantics}
\input{splitting}

>>>>

\documentclass[preprint]{sigplanconf}

@@

\usepackage{amsmath}
%\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{mathpartir}
\usepackage{mathabx}
\usepackage{listings}
\usepackage{hyperref}

\usepackage{cleveref}
\AtBeginDocument{\renewcommand\ref\cref}
\crefname{figure}{Figure}{Figures}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

\input {macros}

@@

\lstset{language=ML,
        columns=fullflexible,
        basicstyle=\ttfamily,
        tabsize=4,
        escapeinside={"*}{*"},
        literate={|->}{{\ $\mapsto$\ }}1
                 {xhat}{{$\hat{\texttt{x}}$}}1
                 {yhat}{{$\hat{\texttt{y}}$}}1
                 {zhat}{{$\hat{\texttt{z}}$}}1
                 {$}{{$\fut$}}1}

@@

%\titlebanner{banner above paper title}        % These are ignored unless
%\preprintfooter{short description of paper}   % 'preprint' option specified.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{intro}

\input{semantics}

\vfill\eject\pagebreak
\input{splitting}

\input{relatedwork}
